R for Clinical Study Reports and Submission

### 2021-10-07 slides/workshop-slides.Rmd

@@

- `r2rtf`: an R package to create production ready tables and figures in RTF format.
The R package is designed to 
  + `r2rtf` Introduction: https://r4csr.org/overview.html#r2rtf

>>>>

## Disclaimer

- All opinions expressed are those of the presenter and not 
  Merck Sharp & Dohme Corp., a subsidiary of Merck & Co., Inc., Kenilworth, NJ, USA.

- Some slides need to be scrolled down to see the full content.

@@

- `r2rtf`: an R package to create production ready tables and figures in RTF format.

## r2rtf Motivation

In the pharmaceutical industry, RTF/Microsoft Word play a central role 
in preparing clinical study reports

Different organization can have different table standards

- E.g., Table layout, Font size, Border type, Footnote, Data source

`r2rtf` is designed to:

- Generate highly customized tables
- Limit package dependency
- Target regulatory deliverables   
- Support pipes (`%>%`)

- `r2rtf` Introduction: https://r4csr.org/overview.html#r2rtf
